Unified Linear Speedup Analyses of Communication-Efficient Stochastic FedAvg and Nesterov FedAvg

### 2021-07-12 source/main.tex
Update on Overleaf.

\newpage
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_zhaonan.jpg}}]{Zhaonan Qu}
Zhaonan Qu is a PhD student in the Department of Economics at Stanford University. His research interest is at the intersection of optimization, machine learning, and causal inference. He received a B.S. in mathematics from Princeton University and an M.A. in mathematics from NYU's Courant Institute.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_kaixiang.png}}]{Kaixiang Lin}
Dr. Kaixiang Lin is an applied scientist at Amazon Lab 126. Before joining Amazon, 
Kaixiang received his Ph.D. degree in Computer Science at Michigan State University in 2020. 
\end{IEEEbiography}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_zhaojian.png}}]{Zhaojian Li}
Dr. Zhaojian Li is an assistant Professor in the Department of Mechanical Engineering at Michigan State University. His main research interests include Robotics and Autonomous Vehicles, Intelligent Transportation System, Reinforcement Learning, Vehicle Dynamics, and Optimal Control.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_jiayu.png}}]{Jiayu Zhou}
Dr. Jiayu Zhou is an assistant professor at
 Department of Computer Science and Engineering, Michigan State University.
 Before joining MSU, Jiayu was a staff research scientist at Samsung Research
 America. Jiayu received his Ph.D. degree in computer science at Arizona
 State University in 2014. 
\end{IEEEbiography}

>>>>

\newpage
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_zhaonan.jpg}}]{Zhaonan Qu}
Zhaonan Qu is a PhD student in the Department of Economics at Stanford University. His research interests include optimization, machine learning, and causal inference. He received a B.S. in mathematics from Princeton University and an M.A. in mathematics from NYU's Courant Institute.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_kaixiang.png}}]{Kaixiang Lin}
Dr. Kaixiang Lin received his Ph.D. degree in Computer Science at Michigan State University in 2020. He regularly serves as a program committee member or reviewer for top-tier machine learning/data ming conferences/journals, including Neurips, ICML, ICLR, TKDE, etc.
% Before joining MSU, he received the B.S. degree from the University of Science and Technology of China, Hefei, China, in 2014. 
\end{IEEEbiography}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_zhaojian.png}}]{Zhaojian Li}
Dr. Zhaojian Li is an assistant Professor in the Department of Mechanical Engineering at Michigan State University. His main research interests include Robotics and Autonomous Vehicles, Intelligent Transportation System, Reinforcement Learning, Vehicle Dynamics, and Optimal Control. He is a senior member of IEEE and recipient of NSF CAREER Award.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_jiayu.png}}]{Jiayu Zhou}
Dr. Jiayu Zhou is an Associate Professor in the Department of Computer Science and Engineering at Michigan State University. He received his Ph.D. degree in computer science from Arizona State University in 2014. Dr. Zhou has a broad research interest in large-scale machine learning, data mining, and biomedical informatics, with a focus on the transfer and multi-task learning. His research has been funded by the National Science Foundation, National Institutes of Health, and Office of Naval Research, and published more than 100 peer-reviewed journal and conference papers in data mining and machine learning. Dr. Zhou is a recipient of the National Science Foundation CAREER Award (2018). His papers received the Best Student Paper Award in 2014 IEEE International Conference on Data Mining (ICDM), the Best Student Paper Award at the 2016 International Symposium on Biomedical Imaging (ISBI), and Best Paper Award at 2016 IEEE International Conference on Big Data (BigData).
\end{IEEEbiography}
